---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dhsclogger

dhsclogger provides a convenience wrapper to the family of `futile.logger`
functions to promote use of standardised logging. For more information
see the `futile.logger` [documentation](https://github.com/zatonovo/futile.logger)

## Installation

You can install the development version of dhsclogger like so:

``` r
remotes::install_github("DataS-DHSC/dhsclogger")
```

## Example usage

To create a log for use in your code:

```{r example}
library(dhsclogger)

# get logger collection
log <- get_dhsc_logger()

# set threshold of console log to warnings and above
log$set_threshold("log.console", "WARN")

# below will only be printed to the log file
log$info("Script started")

```

## Licence

Unless stated otherwise, the codebase is released under the MIT License. This 
covers both the codebase and any sample code in the documentation. The 
documentation is © Crown copyright and available under the terms of the [Open 
Government 3.0 licence](https://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/).
